Exploration in Target Speaker Extraction using Discrete Representations and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-03 src/paper.tex
update

\title{Exploration in Target Speaker Extraction using Discrete Representations 
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

Unlike blind speech separation, which focuses on separating each utterance from a mixture 
of known speakers, target speaker extraction aims at only extracting the 
target speaker's voice given another auxiliary information of the target speaker. Due to the 
development of Deep Neural Network (DNN), many models nowadays are discriminative models. They 
utilize a masking strategy to minimize the distance between the clean speech and estimated 
speech directly \cite{luo2019conv,spex_plus,sepformer,sef_net}. However, these discriminative 
models may not generalize well to unseen data and might even introduce unwanted distortions \cite{distortion}.

>>>>

\title{Exploration in Target Speaker Extraction using Discrete Representations and Language Models
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

Unlike blind speech separation, which focuses on separating each utterance from a mixture 
of known speakers, target speaker extraction aims at only extracting the 
target speaker's voice given another auxiliary information of the target speaker. Due to the 
development of Deep Neural Network (DNN), many models nowadays are discriminative models. They 
utilize a masking strategy to minimize the distance between the clean speech and estimated 
speech directly \cite{luo2019conv,spex_plus,sepformer,sef_net}. However, these discriminative 
models may not generalize well to unseen data and might even introduce unwanted distortions \cite{distortion}. To solve these issues, researchers have proposed generative models. This method aims to learn the underlying distribution of the target speaker's voice and use this knowledge to generate the clean speech of the target speaker from a mixture of voices rather 
than directly mapping from mixed speech to clean speech. Some generative models, like diffusion
models \cite{target_diff} and variational autoencoders (VAE) \cite{vae} have been studied. It has been demonstrated that generative models can achieve results comparable to those of discriminative models \cite{target_diff,tokensplit}.

Recently, self-supervised Learning (SSL) models like HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated
excellent performances on many downstream tasks \cite{superb}. These SSL models extract  
continuous representations containing rich semantic and timbre information of a given speech.
